Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2024-03-05 Edith Zemanick/Sweat Test/sweat_test_analysis.Rmd
sweat test analysis formatting

>>>>

### By genotype severity (CF only)

```{r results='asis'}
t1 <- tableby(
  geno_risk ~ Cl + Na + `Na/Cl Ratio` + `Sweat Chloride Group`,
  data = t1_df[t1_df$Diagnosis == "Cystic Fibrosis", ], control = mycontrols,
)
summary(t1,
  pfootnote = T,
  labelTranslations = labels
)
```

### Pairwise comparisons

Pairwise comparisons using Wilcoxon rank sum test with continuity correction

```{r}
pairwise.wilcox.test(t1_df$Cl, t1_df$Diagnosis, p.adjust.method = "fdr")
pairwise.wilcox.test(t1_df$Na, t1_df$Diagnosis, p.adjust.method = "fdr")
pairwise.wilcox.test(t1_df$`Na/Cl Ratio`, t1_df$Diagnosis, p.adjust.method = "fdr")
```
